Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-08-02 reports/manuscript.Rmd
Add Table 1 to manuscript file

```{r, load-targets}
targets::tar_load(
  c("manuscript_info", "combined_bib", "combined_effects"),
  store = here::here("_targets")
)
ce <- combined_effects
```

@@

>>>>

```{r, load-targets}
targets::tar_load(
  c("manuscript_info", "combined_bib", "combined_effects", "table_rob_latex"),
  store = here::here("_targets")
)
ce <- combined_effects
```

@@

```{r table1, echo = FALSE}
table_rob_latex
```
